\documentclass[a4paper,10pt]{article}

% Useful Packages
\usepackage{marvosym, verbatim}
\usepackage{xunicode,xltxtra,url,parskip} 	% other packages for formatting
\RequirePackage{color}
\usepackage[big]{layaureo} 				% better formatting of the A4 page
\usepackage{titlesec}					% custom \section
\usepackage{fontspec}
\usepackage{setspace}

% Setup hyperref package, and colors for links
\usepackage{hyperref}
\definecolor{links}{rgb}{0,0.15,0.6}
\hypersetup{colorlinks,linkcolor=,urlcolor=links}

% Fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}

% Tweak a bit the margin
\addtolength{\voffset}{-1.4cm}
\addtolength{\textheight}{2.8cm}
\addtolength{\hoffset}{-1.3cm}
\addtolength{\textwidth}{2.6cm}

% Custom titles
\titleformat{\section}{\vspace{-0.5mm}\Large\scshape\raggedright}{}{0em}{}[{\titlerule[.8pt]}]
\titleformat{\subsection}{\scshape\raggedright}{}{0em}{}[{\titlerule[.4pt]}]
\titlespacing{\section}{0pt}{0pt}{0pt}
\titlespacing{\subsection}{0pt}{2pt}{2pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}
\pagestyle{empty} % non-numbered pages
\font\fb=''[cmr10]'' % for use with \LaTeX command
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{0}

\definecolor{light-gray}{gray}{0.1}
\color{light-gray}

%--------------------TITLE-------------------------------
\newcommand{\email}[0]{\href{mailto:brandcomin@gmail.com}{brandcomin@gmail.com}}
\newcommand{\github}[0]{\href{https://github.com/BrandonComins}{github.com/BrandonComins}}
\newcommand{\phone}[0]{(818) 564-9626}
\newcommand{\titlesep}[0]{ • }
\newcommand{\titlename}[2]{\par{\centering{\Huge #1 \textsc{#2}}\par}}
\newcommand{\info}[1]{\centering{\ensuremath{\overline{\underline{\mbox{#1}}}}}}
\titlename{Brandon}{Comins}
\info{\email\titlesep\phone\titlesep\github}


%--------------------CUSTOM OPERATORS--------------------
\newcommand{\term}[1]{\texttt{\uppercase{#1}}}

\newcommand{\resumeSec}[2]{\section{#1}\begin{tabular}{@{}p{50pt}|p{\columnwidth-50pt-2\tabcolsep}@{}}#2\end{tabular}}
\newcommand{\sectionNL}[0]{\\\multicolumn{2}{c}{}\vspace{1.5mm}\\}
\newcommand{\smallNL}[0]{\\\multicolumn{2}{c}{}\vspace{1mm}\\}
\newcommand{\entryNL}[0]{\\\vspace{1mm}\\}
% usage \workEntry{time}{position and workplace}{location}{extra detail}{content}
\newcommand{\workEntry}[5]{\raggedleft\textsc{#1}&\textbf{#2} #3\entryNL\raggedleft\footnotesize{#4}&\small{#5}}
% usage \projEntry{time}{title}{languages}{content}
\newcommand{\projEntry}[4]{\raggedleft\textsc{#1}&\textbf{#2} \textsc{#3}\entryNL&\small{#4}}
% usage \expEntry{time}{experience}
\newcommand{\expEntry}[2]{\raggedleft\textsc{#1}\vspace{-1mm}& \small #2}

%--------------------SECTIONS----------------------------
\resumeSec{Work Experience}{
\smallNL

\workEntry{2022}{Code Coach at theCoderSchool}{Irvine, CA}{}{
Taught as a Code Coach at theCoderSchool, where I had the opportunity to teach elementary and middle school students how to code using Python, Scratch, and Java. Developed strong communication and instructional skills by effectively explaining complex programming concepts in a way that was accessible to students of all skill levels.
}
\sectionNL

\workEntry{2021}{Robotics Teacher for RoboQ}{Online}{}{
Served as a remote Robotics Teacher for high school students, focusing on Arduino robotics. Led instructional sessions on programming, soldering, and computer-aided design (CAD). Strengthened communication skills by ensuring each student comprehended the material and providing tailored support to meet individual needs.
}
\sectionNL

%\workEntry{2015-2018}{Tech Department at Green Polishing Solutions}{Canoga Park, CA}{}{
%Set up, repaired, and maintained the company’s servers, computers, and printers- mostly involving installing software, removing viruses, and swapping parts. 
%}

}

\resumeSec{Projects}{
\smallNL


\projEntry{2022}{Desktop Pet}{Python
{\href{https://github.com/BrandonComins/Desktop-Pet}{\color{links}{github.com/BrandonComins/Desktop-Pet}}}}{
Developed an engaging desktop pet application with a unique feature: the pet occasionally steals the user's mouse when left idle. This project enhanced my proficiency in Python and provided valuable experience working with the tkinter library.
}
\sectionNL


\projEntry{2020}{Drone}{C/C++
{\href{https://github.com/BrandonComins/Eng-7B-Drone}{\color{links}{github.com/BrandonComins/Drone}}}}{
Participated in a class competition where I successfully constructed a drone equipped with sensors to determine optimal moments for deploying a servo-actuated payload. Overcoming initial challenges with aerodynamics, I iteratively redesigned and rebuilt the drone four times until achieving flight capability. Secured 3rd place among 50+ competing groups, demonstrating perseverance and technical competence.
}
\sectionNL

\projEntry{2019}{Rocket Flight Computer}{C/C++
{\href{https://github.com/BrandonComins/Rocket}{\color{links}{github.com/BrandonComins/Rocket}}}}{
Led the construction of a custom flight computer for a high school rocketry project, which logged data and utilized sensors to determine optimal parachute deployment. Pioneered the use of a self-built flight computer, becoming the first student in the school's history to tackle this challenge instead of relying on a commercially available solution. Developed essential skills in problem-solving through debugging, wire management, soldering, and gained valuable knowledge about MOSFETs.
 }
\sectionNL

\projEntry{2019}{Fruit Piano}{C/C++
{\href{https://github.com/BrandonComins/FruitPiano}{\color{links}{github.com/BrandonComins/FruitPiano}}}}{
Participated in a science fair at Darby Elementary School, showcasing STEM and robotics concepts. Developed a creative project called the "Fruit Piano," demonstrating the fun and engaging aspects of wiring and electronics. Explored unconventional methods, such as using fruit, to complete wiring circuits..
}
\sectionNL

\projEntry{2019}{RC Car}{C/C++
{\href{https://github.com/BrandonComins/RC-Car}{\color{links}{github.com/BrandonComins/RC-Car}}}}{
Led the construction of a remote-controlled car using Arduino, aiming to inspire children by demonstrating the enjoyable side of robotics. This project provided hands-on experience with speed controllers and introduced me to the implementation of a Bluetooth module for wireless control.
}
\sectionNL

%\projEntry{2015-2019}{FRC Robotics}{Java
%{\href{https://github.com/team4element}{\color{links}{github.com/team4element}}}{
%Contributed as a member of the First Robotics Competition (FRC) team, assuming the responsibility of programming the robot. Successfully implemented motor control using an Xbox controller in %teleoperation mode, demonstrating precise actuation. Additionally, developed autonomous capabilities for the robot, enabling it to perform vision tracking and pathfinding tasks..
%}

}


\resumeSec{Technical Skills and Qualifications}{
\smallNL
\raggedleft Languages& \textsc{Java, Python, C++, C, Verilog, VHDL, MIPS Assembly, Regex, Embeded Systems, Latex, React}
\smallNL
\raggedleft Software& Xilinx Vivado, Git, Visual Studio, MATLAB, Solidworks, Simplify3D, Arduino, ROS2
}

\begin{tabular}{@{}p{.65\textwidth}p{.35\textwidth-2\tabcolsep}@{}}
\resumeSec{Education}{
\sectionNL
\workEntry{2019-2023}{University of California, Irvine}{Irvine, CA}{}{
Graduated in June 2023, \textsc{Computer Science Engineering B.S}}
\smallNL
\workEntry{2019}{Los Angeles Pierce College}{Woodland Hills, CA}{}{
Concurrent enrollment with high school}}
&
\section{Relevant Coursework}
\vspace{1.7mm}\raggedright\small
% Electrical,
Electrical Devices and Systems,
Organization of Digital Computers,
%Programming
Python Programming,
Advanced C,
Data Structures,
Intro to computer graphics,
Discrete Mathematics \& Probability Theory,
Linear Algebra \& Differential Equations,
Calculus 3,
% ETC
Intro to Software Engineering
\end{tabular}

\resumeSec{Additional Experience}{
\smallNL

\expEntry{2022}{Software Lead for Legacy Robotics, UCI's Robomaster University  League's Team}
\smallNL
\expEntry{2020-2022}{Mentor High Tech Los Angeles in FRC (First Robotics Competition)}
\smallNL
\expEntry{2019}{Computer Teacher at One Generation}
\smallNL
\expEntry{2019}{Team Captain of High School FRC team (First Robotics Competition)}
\smallNL
\expEntry{2019}{Mentor Darby Elementary in Lego Robotics (First Lego League)}
\smallNL
\expEntry{2018}{Camp Counselor for Lego Robotics Camp}
\smallNL
\expEntry{2016-2018}{Volunteer at Motion Picture Funding Hospital}
\smallNL
%\expEntry{2015-2018}{Tech Department at Green Polishing Solutions}

}
\end{document}